### 2015-01-31 docs/report/intro.tex
Initial serialization doc

\section*{Introduction}
In 1965 Gordon Moore proposed the popularly known "Moore's law" \cite{moore65}, which predicts that the number of transitors in integrated circuits will double every two years.
As a consequence, programs that use a single processor/core will automatically become faster without the need to modify them with that purpose in mind.

@@

>>>>

\section{Introduction}
In 1965 Gordon Moore proposed the popularly known "Moore's law" \cite{moore65}, which predicts that the number of transitors in integrated circuits will double every two years.
As a consequence, programs that use a single processor/core will automatically become faster without the need to modify them with that purpose in mind.

@@

\pagebreak

### 2015-01-31 docs/report/micro_benchmarks.tex
Initial serialization doc

\section*{About Microbenchmmarks}
A common practice to measure the performance of a fragment of code, or to compare it to the performance of some other code fragment is to create a micro benchmark. Throughout this document, there are multiple references to benchmarks of this kind since their results helped us make decision about how to implement some specific library features.

@@

Alternatively it could notice that the variable \textit{j} is not being used so it could just throw the line away. In any case, we would just be measuring how long it takes for JavaScript to execute the loop, which is not what we want. To verify that is not the case the tool IRHydra can be used \cite{ir-hydra}, which \textit{can display intermediate representations used by V8}. As shown in the following figure, v8 inline the function (the blue chevron marks that) but the loop invariant was not detected and optimized:
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{naive_benchmark_ir_hydra}
  \caption{Optimized benchmark code with inlined function.}
\end{figure}

>>>>

\section{About Microbenchmmarks}
A common practice to measure the performance of a fragment of code, or to compare it to the performance of some other code fragment is to create a micro benchmark. Throughout this document, there are multiple references to benchmarks of this kind since their results helped us make decision about how to implement some specific library features.

@@

Alternatively it could notice that the variable \textit{j} is not being used so it could just throw the line away. In any case, we would just be measuring how long it takes for JavaScript to execute the loop, which is not what we want. To verify that is not the case the tool IRHydra can be used \cite{ir-hydra}, which \textit{can display intermediate representations used by V8}. As shown in the following figure, v8 inline the function (the blue chevron marks that) but the loop invariant was not detected and optimized:
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{naive_benchmark_ir_hydra}
  \caption{Optimized benchmark code with inlined function.}
\end{figure}
\pagebreak
